Approximation as Differentiation

### 2025-04-01 notes/sec/cmon-enriched.tex
CMon-enriched functors also preserve bilinear composition.
But the fact that F preserves bilinear composition is derivable rather than a requirement on F.
Defining your 'basic' Yoneda embedding.

For any monoidal category $V$ and $V$-enriched categories $C$ and $D$, the action of a \emph{$V$-enriched}
functor $F: C \to D$ on morphisms takes the form of a morphism $C(X,Y) \to D(F(X),F(Y))$ between hom-objects
in $V$. In the specific setting of a $\CMon$-enriched presheaf $F: C^\op \to \CMon$, this means that $F$
preserves the additive structure of morphisms:
\begin{itemize}
\item $F(0_{X,Y}) = 0_{F(Y),F(X)}$
\item $F(f + g) = F(f) + F(g)$
\end{itemize}
and also preserves bilinear composition, i.e.:
\begin{itemize}
\item $F(f + g) \comp F(h) = F(h \comp f) + F(h \comp g)$
\item $F(h) \comp F(f + g) = F(f \comp h) + F(g \comp h)$
\end{itemize}
in addition to the usual functorial properties.

>>>>

For any monoidal category $V$ and $V$-enriched categories $C$ and $D$, the action of a \emph{$V$-enriched}
functor $F: C \to D$ on morphisms takes the form of a morphism $C(X,Y) \to D(F(X),F(Y))$ between hom-monoids
in $V$. In the specific setting of a $\CMon$-enriched presheaf $F: C^\op \to \CMon$, this means that $F$
preserves the additive structure of morphisms:
\begin{itemize}
\item $F(0_{X,Y}) = 0_{F(Y),F(X)}$
\item $F(f + g) = F(f) + F(g)$
\end{itemize}
It then follows automatically that $F$ also preserves bilinear composition, i.e.:
\begin{itemize}
\item $F(f) \comp F(0) = F(f) = F(0) \comp F(f)$
\item $F(f + g) \comp F(h) = F(h \comp f) + F(h \comp g)$
\item $F(h) \comp F(f + g) = F(f \comp h) + F(g \comp h)$
\end{itemize}
in addition to the usual functorial properties.

\subsubsection{$\CMon$-enriched Yoneda embedding}

Suppose $C$ a small category. The standard \emph{Yoneda embedding} for $C$ is the functor $\Yoneda: C \to
\Func{C^\op}{\Set}$ sending:
\begin{itemize}
\item any object $X$ in $C$ to the contravariant hom-functor $C(-,X)$ which sends:
\begin{itemize}
\item any object $Y$ in $C$ to the hom-set $C(Y,X)$
\item any morphism $f: Y \to Z$ in $C$ to the pre-composition function $(- \comp f): C(Z,X) \to C(Y,X)$
\end{itemize}
\item any morphism $f: X \to Y$ in $C$ to the natural transformation
\end{itemize}
